Actuator line modeling of vertical-axis turbines

### 2016-08-27 paper.tex
Make new figure to show computational domain

    \includegraphics[width=0.65\textwidth]{thesis_alm-mesh}

    \caption{$x$--$y$ planar slice of the mesh used for the ALM RANS
        simulations.}

>>>>

    \includegraphics[width=0.8\textwidth]{alm-domain}

    \caption{Computational domain used for the RANS ALM simulations. All
    dimensions are in meters, flow is oriented in the $+x$-direction, and the
    cylindrical region represents the swept area of the UNH-RVAT rotor. Note
    that increased mesh refinrement was used for the LES simulations.}
